Sample variance in weak lensing: how many simulations are required?

### 2016-01-09 Paper/paper.tex
Paper/paper.tex

%ZH: I changed to more catchy title:
%\title{Simulating sample variance in weak lensing: effects on parameter inferences}
%AP: Ok

@@

%However, we find that in practice, a larger number of
%simulations might be needed to measure accurate feature means and to
%avoid parameter biases.
%ZH: I am not sure about the last sentence. I believe it is based on
%    an overly stringent reading of Fig.2, and that in fact we could
%    claim here, instead, that N_s=2 simulations are also sufficient
%    to get the correct mean.
%    See my comments at the end of the Conclusion section.

%AP: Ok, sentence removed

@@

\section{Introduction}
%
Weak gravitational lensing (WL) is a promising cosmological probe for
constraining the dark energy equation of state $w$, and has been
considered by a range of past (CFHTLens \citep{cfht1,cfht2}, COSMOS \citep{cosmos}),
%ZH: also cite COSMOS survey here...
%AP: done
ongoing (DES \citep{DES}) and future (LSST \citep{LSST}, Euclid \citep{Euclid}, WFIRST \citep{WFIRST})
%ZH: also cite Euclid and WFIRST.
%AP: done
experiments. In an era where cosmology is data driven, accurate
numerical simulations of shear fields are becoming important for
several reasons, including the study of baryonic effects
\citep{BaryonXiuyuan,BaryonSemboloni,BaryonsWhite,BaryonsKnox,BaryonsZentner1,BaryonsZentner2}, 
%ZH: also cite Joop Schaye's hydro-simulation papers on lensing (Semboloni et al), and earlier papers by Martin White et al...  Lloyd Knox et al... and Zentner et al... (I think all of these are in Xiuyuan's paper).
%AP: done
the computation of non--Gaussian statistics
\citep{PeaksJan,MinkJan,MinkPetri,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich} 
%ZH: Add here some citations of other groups - Marian+Bernstein.... Bhuvnesh Jain et al... Refregier et al... Dietrichh+Hartmann... Shirasaki+Yoshida.. (again just copy from our previous papers).
%AP: done
and the  assessment of various systematics
\citep{MinkShirasaki,Sys-Bard,Sys-Chang,Sys-Huterer}.
%ZH: cite papers by Jan+Morgan+Bard... and also Chihway Chan...Shirasaki+Yoshida.. and older ones by Dragan Huterer on photo-z errors..
%AP: done

A fundamental issue with predictions from simulations is that the
finite number of simulations naturally introduces fluctuations in the
forecasts, due to inevitable sample variance~\footnote{Sample variance is a broad term that has been used in the literature to describe a range of phenomena.  Throughout this paper, we use it to refer to the fluctuations in an ensemble of simulations, which represent random realizations of the same initial conditions.}.
%ZH: I think 'cosmic variance' usually refers to observations of the actual sky (which is finite). 
%AP: OK 
In general, quantities such as the mean or the variance of any feature
(e.g. the shear power spectrum at a multipole $\ell$), measured from a
finite set of simulations, will fluctuate, and can also suffer a bias.
While biases in the estimates of both the mean and the variance have
been studied extensively, the impact of fluctuations in the variance
has received comparatively less attention.  These fluctuations have,
however, been shown to have non-negligible effects on estimates of
features covariance matrices and hence on parameter constraints. In
particular, in the limit of Gaussian fluctuations, the parameter
confidence limits are degraged by a factor
$1+O(1/N_r)$~\citep{DodelsonSchneider13,Taylor12}.
%MM: also cite Taylor Joachimi and Kitching
%AP: done

This work studies these issues further, focusing on the number of
independent $N$--body simulations required for an accurate estimate of
the parameter constraints.  Ray-tracing simulations that resolve the
cosmic structures responsible for lensing on arcminute scales are
limited to physical sizes of hundreds of Mpc, and thus cover a solid
angle of only $O(10$ deg$^2)$.  As a result, many simulations are
required to tile a significant fraction of the sky, and to make
predictions for large ``all-sky'' surveys, such as the ones by DES,
LSST, Euclid, WFIRST.  In practice, this has led to the wide-spread
use of ``pseudo-independent'' realizations, i.e. a procedure in which
one randomizes and re-cycles the output of a single 3D simulation
multiple times.
%ZH: Add citations here of papers resorting to this technique
In light of the forthcoming large surveys, it is imperative to assess
the statistical validity of this approach, and to ask how many times a
single simulation can be fairly recycled.  In this paper, we address
these questions with ensembles of up to $N_r=10^5$ random
realizations, extracted from up to $N_s=200$ independent ray-tracing
N-body simulations. We focus in particular on the parameter $w$, and
on two different statistics: the (convergence) power spectrum and
the number counts of peaks.

@@

\subsection{Ray-tracing simulations of the convergence field}
\label{shearsim}
%
In this section, we describe how we constructed our shear field
ensembles. Background galaxies at redshift $z_s$ are lensed by large
scale structures between $z=0$ and $z_s$. The shape distortions due to
the cosmic shear $\pmb{\gamma}$ can be computed in terms of the dark
matter gravitational potential $\Phi(\bb{x},z)$. Because the evolution
of $\Phi$ with redshift is non--linear, it needs to be computed with
numerical simulations. We make use of the public code \texttt{Gadget2}
\citep{Gadget2}, with which we run a sequence of $200$ independent
dark--matter--only $N$--body simulations that track the evolution of
the density fluctuations. We assume a standard $\Lambda$CDM background
universe with the parameters
$(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$.
We fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$,
and use $512^3$ particles, corresponding to a Dark Matter particle mass of
$\approx 10^{10}M_\odot$.
%ZH: ``mass resolution'' here means DM particle mass ?
%AP: fixed

We assume a uniform galaxy distribution at a constant redshift $z_s=2$
(at which the simulation box has an angular size of $\theta_{\rm
  box}=3.5\mathrm{deg}$) and we discretize the mass distribution
between $z_s$ and the observer at $z=0$ with a sequence of 46 two
dimensional lenses of thickness $80\mathrm{Mpc}/h$. The surface
density on each lens plane is computed by projecting the
three--dimensional density measured from \texttt{Gadget2}
snapshots. We then apply the multi--lens--plane algorithm (see
\citep{RayTracingHartlap,RayTracingJain} for example) to trace the
deflections of $n_{\rm ray}^2=2048^2$ light rays arranged on a square grid
of total size $\theta_{\rm box}$, from $z=0$ to $z_s$. Our
implementation of this algorithm is part of the \texttt{LensTools}
computing package we have been developing \citep{LensTools}, and have
released under the \texttt{MIT} license. Many different realizations
$r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be
generated by picking different lens planes that lie between the
observer and $z_s$. The randomization procedure we adopt is the
following (see \citep{Sato12} for reference):
%ZH: we should cite some paper here. We didn't invent most of this
%procedure ourselves (except for maybe the 3-times thicker simulation
%output, and the random mixing of the planes from different N-body sims ?).
%AP: I added the citation to Sato et. al, which refer to this procedure without citing anyone

\begin{itemize}
\item For each lens-plane redshift $z_l$, select the snapshot at $z_l$ from the $i$--th $N$--body simulation, where $i$ is a random integer $i\in [1,N_s]$.
\item Choose randomly between the three orthogonal directions ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be perpendicular to this direction.
\item Choose the position of the plane along the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$. This gives a total of 9 choices for generating a lens plane out of a single $N$--body snapshot.
\item Perform a periodic random shift of the lens plane along its two directions.
%ZH: should we specify the range of the random shifts (0 to 1/2 the lens plane dimension?)
%AP: This is not necessary, since the shifts are periodic, in principle one could choose a random number of pixels. In particular this number should be between 0 and 4095, because each lens plane has 4096 pixels
\item Repeat the above procedure for each lens-plane redshift $z_l$.
\end{itemize}  
%
This randomization procedure allows us to produce an (almost)
arbitrary number $N_r$ of shear realizations
$\pmb{\gamma}_r(\pmb{\theta})$. However, these realizations are not
guaranteed to be independent, if $N_s$ is not large enough. Using the
set of 200 independent $N$--body simulations, we construct different
ensembles with different choices of $N_s\in[1,200]$. Each of these
ensembles consists of the same number $N_r=1000$ of shear
realizations. We also build an additional ensemble with $N_s=1$ and
$N_r=10^5$ realizations. For each realization of each ensemble, we
reconstruct the convergence $\kappa_r(\pmb{\theta})$ from the trace of the light ray deflection Jacobian matrix, measured looking at the difference in angle deflection between nearby light rays \citep{RayTracingHartlap,RayTracingJain,Sato12}.
%ZH: we should add 2 sentences on how you measured kappa.  Directly from the ray-tracing?
%   (but above, when you discuss ray-tracing, you mention only gamma).  Or did you do 
%    Kaiser-Squires on the gamma field ? 
%AP: done, we measure kappa directly from the ray tracing

We measure the $\kappa$ angular power spectrum $P^{\kappa\kappa}_r(\ell)$ defined as
\begin{equation}
\langle\tilde{\kappa}_r(\pmb{\ell})\tilde{\kappa}_r(\pmb{\ell}')\rangle = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}_r(\ell)
\end{equation}
%
As an additional summary statistic, we consider the counts of local
$\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
(hereafter \textit{peak counts}), with varying $\kappa_0$ chosen between the minimum and maximum values measured from the maps $(\kappa_{\rm min},\kappa_{\rm max})=(-0.06,0.45)$. Different choices of $\kappa_0$ binning used in this work are outlined in Table \ref{featuretable}. 
%ZH: state here the range and binning choice of $\kappa_0$
%AP: done
The fact that the ensemble of $N_r$ realizations is not completely
independent if $N_s$ is not large enough can have an effect on the
covariance estimators of both $P^{\kappa\kappa}$ and $n(\kappa_0)$.

%ZH: it would be logical to mention the other w,Sig,Om, sims here, and point to \ref{simtable})
%AP: done, added the below

To measure the cosmological dependence of the $\kappa$ peak counts, we also performed additional ray--tracing simulations with different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$. A summary of the complete set of shear ensembles used in this work is outlined in Table \ref{simtable}.

\subsection{Cosmological parameter inference}
%
Let $\bbh{d}$ be a single estimate for a feature of dimension $N_b$, 
%ZH: ``Hat'' here refers to an estimator?
%AP: Yes: quantities without the hat are the expectation values 
$\bb{d}(\bb{p})$ be the
%smooth expectation
%ZH: I believe ``smooth expectation'' means true mean value, yes?
%AP: yes
true value of this feature at a point $\bb{p}$ in parameter space
(which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$
feature covariance matrix. For the purpose of this work $\bb{p}$ is
the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the
features -- either a power spectrum or a peak count histogram -- in Table
\ref{featuretable}. Although existing emulators (see
\citep{coyote2,Nicaea,SchneiderKnoxCovariance} for example) can be used to compute $\bb{d}(\bb{p}),\bb{C}$ in some cases, this is not true in the general case. 
%ZH: I am missing the point here.  Why is covariance matrix ``more complicated'' ?
%    Even to estimate a mean, one has to ``generate a series of mock realizations''.
%    Unless you are willing to equate a single realization as the mean.   But then
%    by the same logic, you could estimate the covariance matrix from two realizations.
%    Please clarify what you mean...  maybe I am missing something?  Or you simply mean
%    that published emulators usually do not emulate the cov.matrix (even though they could)?
%    Note that there is a paper by Schneider and Knox, in which they do an interpolation of the
%    power spectrum covariance matrix.
%AP: The intended meaning is the latter: published emulators only predict the means. It is also true that getting the covariance accurate is more difficult than getting the means accurate. I rephrased the sentence.
Estimating $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
sample covariance $\bbh{C}$,

@@

\begin{table*}
\begin{center}
\begin{tabular}{c|c|c||c|c}
\toprule
$\Omega_m$ &  $w$ & $\sigma_8$ & $(N_s,N_r)$ & Number of $\kappa$ ensembles \\ \hline \hline
\midrule
%
0.26 & $-$1 & 0.8 & $(1\div200,1024),(1,128000)$ & 16 \\
0.29 & $-$1 & 0.8 & (1,1024) & 1 \\
0.26 & $-$0.8 & 0.8 & (1,1024) & 1 \\
0.26 & $-$1 & 0.6 & (1,1024) & 1 \\
%
\bottomrule
\end{tabular}
\end{center}
\caption{Summary of the shear ensembles used in this work.}
%ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
%    Add the ensemble with N_s=1, N_r=10^5 to this table.
%    Also: point the reader to this table in the text, up front, when the 
%    ensembles are first discussed.
%AP: done
\label{simtable}
\end{table*}

@@

\item Usually the true data covariance is unknown, and it is tempting to plug in its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$. This approach has been used before in the literature (e.g.~\citep{MinkPetri,MinkShirasaki}). If this is done without correcting for the bias in $\bbh{\Psi}$ (see eq.~(\ref{firstmoment}) below or \citep{Taylor12} for reference), 
%ZH: we should probably cite Hartlap et al. and Taylor et al. here for this Psi bias.  (I assume this is what you mean in eq. 19)
%AP: done
the parameter variance will have a contribution from both the second and first-order fluctuations in $\bbh{\Psi}$, which now have a nonzero expectation value. In this case the bias sums up to
%
\begin{equation}
\label{mockscalinguncorrected}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right).
\end{equation}

@@

\end{enumerate} 
%
The error degradation in each parameter $p$, at leading order, scales
as $D/N_r$, where $D=N_b-N_p$, $N_p-N_b$, and $1+N_p$ for cases 1, 2,
and 3, respectively.
%ZH: It was not clear to me what the main point of the text below was. I paraphrased it slightly. OK?
%This means that, when parameter errors are
%estimated purely from simulations, and the same simulation set is used
%to estimate both $\bbh{C},\bbh{\Psi}$, these errors tend to decrease
%with $N_b$ (case 2), or at best remain constant (case 3), while the
%distribution of $\bbh{p}$ has still a variance that increases with
%$N_b$. This typically leads to underestimates in parameter errors. 
%AP: Not exactly: my point was that the distribution of \bbh{p} has a true variance that increases with Nb, but the estimate of this variance (which we quote as the errorbar) does not increase with Nb. Hence we get the wrong parameter fit (i.e. which excludes the true value at high significance level)
Note that in the last case, which is most relevant when fitting actual data, the estimated degradation turns out to be too optimistic: the parameter estimate $\bbh{p}$ has a variance that grows linearly with $N_b$, but the estimated degradation in eq. (\ref{mockscalingcorrected}) is constant with $N_b$. This can lead to underestimation of error bars, which can be mistakenly interpreted as a parameter bias.  
We derived the scaling relations of the form
%
\begin{equation}
\label{ourscaling}
\langle\h{\sigma}_p^2\rangle = \sigma^2_{p,\infty}(N_s)\left(1+\frac{D}{N_r}\right)
\end{equation}
%
above by assuming that the noise in $\bbh{d}$ is Gaussian. We then directly test these scaling relations using our simulations, in the limits of both high and low $N_r$.
%ZH: It is still a little unclear here what is being tested.  Is it the Gaussianity assumption? I added that.
%    But perhaps you had some other issue in mind.
%AP: The noise in $\bbh{C}$ and $\bbh{\Psi}$ is not Gaussian: if the data vector from which $\bbh{C}$ and $\bbh{\Psi}$ are estimated in Gaussian, then these matrices are distibuted according to, respectively, the Wishart and inverse Wishart distributions. We are testing that the degradation effectively decreases as 1/Nr at leading order.  
We indicate the diagonal elements of $\h{\Sigma}_{\bb{p}}$ as $\h{\sigma}^2_p=\mathrm{diag}(\h{\Sigma}_{\bb{p}})$ 
%ZH: I am confused.  Why is a new symbol \sigma necessary here, on top of \Sigma ?
%    (And also: here you write \Sigma_pp, but above it was denoted \Sigma_p  )
%AP: fixed. I introduced the \sigma symbol for the single parameter variances (as opposed to the full parameter covariance), because these are the quantities we plot
and we indicate by $\sigma^2_{p,\infty}$ the expectation value of the variance of each parameter in the limit of an infinite number of realizations
$N_r\rightarrow\infty$.  We call $D$ the \textit{effective dimensionality} of the feature space (which, as seen before, can be
negative in some pathological cases).
%ZH: I added pathological here.  Do you agree?  It's only negative in case 1, when
%    N_p > N_b (which is impossible -- cannot measure N_p parameters with N_b observables)
%    or in case 2 (when N_b > N_p, so that's OK, but this case ust means we ``forgot'' to correct for the psi-bias).
%AP: agreed
We compute the expectation values of $\h{\sigma}^2_p$
(eqs.~\ref{estimatorcovariance} and \ref{ourscaling}) by
averaging over 100 random resamplings of our shear ensembles. For the
true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use
the estimated covariance from a grand ensemble built with the union of
all the ensembles with different $N_s$.

@@

In this section we discuss our main findings and their
implications. Figure \ref{ps_pdf} shows that, although different
choices of $N_s$ do not affect the power spectrum PDF on large scales
(top two panels), there are some qualitative differences on smaller
scales (bottom two panels). On these smaller scales, shear ensembles
built from $N_s=1$ do not produce the same statistical behavior as
ensembles built with larger $N_s$. In particular, looking at the
black curves, we see that the $N_s=1$ ensembles exibit large shifts
with respect to the other PDFs to lower power, including the locations
of the peaks of the PDFs.  We attribute these offsets to large
(random) statistical errors.
%ZH: I changed the wording above.  We didn't really prove that these are statistical errors,
%    and not some systematic shift to low power when N_s is low.
%AP: OK

>>>>

@@

@@

\section{Introduction}
%
Weak gravitational lensing (WL) is a promising cosmological probe for
constraining the dark energy equation of state $w$, and has been
considered by a range of past (CFHTLens \citep{cfht1,cfht2}, COSMOS
\citep{cosmos}), ongoing (DES \citep{DES}) and future (LSST
\citep{LSST}, Euclid \citep{Euclid}, WFIRST \citep{WFIRST})
experiments. In an era where cosmology is data driven, accurate
numerical simulations of shear fields are becoming important for
several reasons, including the study of baryonic effects
\citep{BaryonXiuyuan,BaryonSemboloni,BaryonsWhite,BaryonsKnox,BaryonsZentner1,BaryonsZentner2},
the computation of non--Gaussian statistics
\citep{PeaksJan,MinkJan,MinkPetri,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich}
and the assessment of various systematics
\citep{MinkShirasaki,Sys-Bard,Sys-Chang,Sys-Huterer}.

A fundamental issue with predictions from simulations is that the
finite number of simulations naturally introduces fluctuations in the
forecasts, due to inevitable sample variance~\footnote{Sample variance
  is a broad term that has been used in the literature to describe a
  range of phenomena.  Throughout this paper, we use it to refer to
  the fluctuations in an ensemble of simulations, which represent
  random realizations of the same initial conditions.}.  In general,
quantities such as the mean or the variance of any feature (e.g. the
shear power spectrum at a multipole $\ell$), measured from a finite
set of simulations, will fluctuate, and can also suffer a bias.  While
biases in the estimates of both the mean and the variance have been
studied extensively, the impact of fluctuations in the variance has
received comparatively less attention.  These fluctuations have,
however, been shown to have non-negligible effects on estimates of
features covariance matrices and hence on parameter constraints. In
particular, in the limit of Gaussian fluctuations, the parameter
confidence limits are degraged by a factor
$1+O(1/N_r)$~\citep{DodelsonSchneider13,Taylor12}.

This work studies these issues further, focusing on the number of
independent $N$--body simulations required for an accurate estimate of
the parameter constraints.  Ray-tracing simulations that resolve the
cosmic structures responsible for lensing on arcminute scales are
limited to physical sizes of hundreds of Mpc, and thus cover a solid
angle of only $O(10$ deg$^2)$.  As a result, many simulations are
required to tile a significant fraction of the sky, and to make
predictions for large ``all-sky'' surveys, such as the ones by DES,
LSST, Euclid, WFIRST.  In practice, this has led to the wide-spread
use of ``pseudo-independent'' realizations, i.e. a procedure in which
one randomizes and re-cycles the output of a single 3D simulation
multiple times.  In light of the forthcoming large surveys, it is
imperative to assess the statistical validity of this approach, and to
ask how many times a single simulation can be fairly recycled.  In
this paper, we address these questions with ensembles of up to
$N_r=10^5$ random realizations, extracted from up to $N_s=200$
independent ray-tracing N-body simulations. We focus in particular on
the parameter $w$, and on two different statistics: the (convergence)
power spectrum and the number counts of peaks.

@@

\subsection{Ray-tracing simulations of the convergence field}
\label{shearsim}
%
In this section, we describe how we constructed our shear field
ensembles. Background galaxies at redshift $z_s$ are lensed by large
scale structures between $z=0$ and $z_s$. The shape distortions due to
the cosmic shear $\pmb{\gamma}$ can be computed in terms of the dark
matter gravitational potential $\Phi(\bb{x},z)$. Because the evolution
of $\Phi$ with redshift is non--linear, it needs to be computed with
numerical simulations. We make use of the public code \texttt{Gadget2}
\citep{Gadget2}, with which we run a sequence of $200$ independent
dark--matter--only $N$--body simulations that track the evolution of
the density fluctuations. We assume a standard $\Lambda$CDM background
universe with the parameters
$(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$.
We fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$,
and use $512^3$ particles, corresponding to a dark matter particle
mass of $\approx 10^{10}M_\odot$.

We assume a uniform galaxy distribution at a constant redshift $z_s=2$
(at which the simulation box has an angular size of $\theta_{\rm
  box}=3.5\mathrm{deg}$) and we discretize the mass distribution
between $z_s$ and the observer at $z=0$ with a sequence of 46 two
dimensional lenses of thickness $80\mathrm{Mpc}/h$. The surface
density on each lens plane is computed by projecting the
three--dimensional density measured from \texttt{Gadget2}
snapshots. We then apply the multi--lens--plane algorithm (see
\citep{RayTracingHartlap,RayTracingJain} for example) to trace the
deflections of $n_{\rm ray}^2=2048^2$ light rays arranged on a square grid
of total size $\theta_{\rm box}$, from $z=0$ to $z_s$. Our
implementation of this algorithm is part of the \texttt{LensTools}
computing package we have been developing \citep{LensTools}, and have
released under the \texttt{MIT} license. Many different realizations
$r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be
generated by picking different lens planes that lie between the
observer and $z_s$. The randomization procedure we adopt is the
following (see \citep{Sato12} for reference):

\begin{itemize}
\item For each lens-plane redshift $z_l$, select the snapshot at $z_l$ from the $i$--th $N$--body simulation, where $i$ is a random integer $i\in [1,N_s]$.
\item Choose randomly between the three orthogonal directions ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be perpendicular to this direction.
\item Choose the position of the plane along the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$. This gives a total of 9 choices for generating a lens plane out of a single $N$--body snapshot.
\item Perform a periodic random shift of the lens plane along its two directions.
\item Repeat the above procedure for each lens-plane redshift $z_l$.
\end{itemize}  
%
This randomization procedure allows us to produce an (almost)
arbitrary number $N_r$ of shear realizations
$\pmb{\gamma}_r(\pmb{\theta})$. However, these realizations are not
guaranteed to be independent, if $N_s$ is not large enough. Using the
set of 200 independent $N$--body simulations, we construct different
ensembles with different choices of $N_s\in[1,200]$. Each of these
ensembles consists of the same number $N_r=1000$ of shear
realizations. We also build an additional ensemble with $N_s=1$ and
$N_r=10^5$ realizations. For each realization of each ensemble, we
reconstruct the convergence $\kappa_r(\pmb{\theta})$ from the trace of
the light-ray deflection Jacobian matrix, measured from the difference
in deflection angles between nearby light-rays
\citep{RayTracingHartlap,RayTracingJain,Sato12}.

We measure the $\kappa$ angular power spectrum $P^{\kappa\kappa}_r(\ell)$ defined as
\begin{equation}
\langle\tilde{\kappa}_r(\pmb{\ell})\tilde{\kappa}_r(\pmb{\ell}')\rangle = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}_r(\ell)
\end{equation}
%
As an additional summary statistic, we consider the counts of local
$\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
(hereafter \textit{peak counts}), with varying $\kappa_0$ chosen
between the minimum and maximum values measured from the maps
$(\kappa_{\rm min},\kappa_{\rm max})=(-0.06,0.45)$. Different choices
of $\kappa_0$ binning used in this work are outlined in Table
\ref{featuretable}.  The fact that the ensemble of $N_r$ realizations
is not completely independent if $N_s$ is not large enough can have an
effect on the covariance estimators of both $P^{\kappa\kappa}$ and
$n(\kappa_0)$.

To measure the cosmological dependence of the $\kappa$ peak counts, we
performed a set of additional ray--tracing simulations with different
combinations of the cosmological parameter triplet
$(\Omega_m,w,\sigma_8)$. A summary of the complete set of shear
ensembles used in this work is listed in Table \ref{simtable}.

\subsection{Cosmological parameter inference}
%
Let $\bbh{d}$ be a single estimate for a feature of dimension $N_b$,
$\bb{d}(\bb{p})$ be the true value of this feature at a point $\bb{p}$
in parameter space (which has a dimension $N_p$) and $\bb{C}$ be the
$N_b\times N_b$ feature covariance matrix. For the purpose of this
work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is
one of the features -- either a power spectrum or a peak count
histogram -- in Table \ref{featuretable}. Although existing emulators
can be used, in principle, to compute both $\bb{d}(\bb{p})$ and
$\bb{C}$, the latter is more difficult, and typically only the mean,
$\bb{d}(\bb{p})$, has been computed to date (refs.~\citep{coyote2,Nicaea}, but see
an exception by ref.~\citep{SchneiderKnoxCovariance}).
%ZH: I am missing the point here.  Why is covariance matrix ``more complicated'' ?
%    Even to estimate a mean, one has to ``generate a series of mock realizations''.
%    Unless you are willing to equate a single realization as the mean.   But then
%    by the same logic, you could estimate the covariance matrix from two realizations.
%    Please clarify what you mean...  maybe I am missing something?  Or you simply mean
%    that published emulators usually do not emulate the cov.matrix (even though they could)?
%    Note that there is a paper by Schneider and Knox, in which they do an interpolation of the
%    power spectrum covariance matrix.
%AP: The intended meaning is the latter: published emulators only predict the means. It is also true that getting the covariance accurate is more difficult than getting the means accurate. I rephrased the sentence.
%ZH2: OK, I rephrased it a bit above to be clearer.  I believe only Schneider et al. did ``C''.
Estimating $\bb{C}$ from simulations involves generating a series of
mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
sample covariance $\bbh{C}$,

@@

\begin{table*}
\begin{center}
\begin{tabular}{c|c|c||c|c}
\toprule
$\Omega_m$ &  $w$ & $\sigma_8$ & $(N_s,N_r)$ & Number of $\kappa$ ensembles \\ \hline \hline
\midrule
%
0.26 & $-$1 & 0.8 & (1 to 200,1024) & 16 \\
0.26 & $-$1 & 0.8 & (1,128000) & 1 \\
0.29 & $-$1 & 0.8 & (1,1024) & 1 \\
0.26 & $-$0.8 & 0.8 & (1,1024) & 1 \\
0.26 & $-$1 & 0.6 & (1,1024) & 1 \\
%
\bottomrule
\end{tabular}
\end{center}
\caption{Summary of the shear ensembles used in this work. $N_s$ and
  $N_r$ refer to the number of independent N-body simulations, and the
  number of pseudo-independent realizations created from these
  simulations, respectively.}
%ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
%    Add the ensemble with N_s=1, N_r=10^5 to this table.
%    Also: point the reader to this table in the text, up front, when the 
%    ensembles are first discussed.
%AP: done
%ZH2: The first raw was a bit confusing, so I separated it into two rows. Also added words to the caption
%    (also, the N_r=10^5 one is the 17th ensemble, in addition to the 16 you listed here before, no? So 16 should have been 17?)
\label{simtable}
\end{table*}

@@

\item Usually the true data covariance is unknown, and it is tempting
  to plug in its estimator $\bbh{C}$, measured from the same
  simulation set we use to compute $\bbh{\Psi}$. This approach has
  been used before in the literature
  (e.g.~\citep{MinkPetri,MinkShirasaki}). If this is done without
  correcting for the bias in $\bbh{\Psi}$ (see Ref.~\citep{Taylor12}
  and eq.~\ref{firstmoment} below), the parameter variance will have a
  contribution from both the second and first-order fluctuations in
  $\bbh{\Psi}$, which now have a nonzero expectation value. In this
  case the bias sums up to
%
\begin{equation}
\label{mockscalinguncorrected}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right).
\end{equation}

@@

\end{enumerate} 
%
The error degradation in each parameter $p$, at leading order, scales
as $D/N_r$, where $D=N_b-N_p$, $N_p-N_b$, and $1+N_p$ for cases 1, 2,
and 3, respectively.
%ZH: It was not clear to me what the main point of the text below was. I paraphrased it slightly. OK?
%This means that, when parameter errors are
%estimated purely from simulations, and the same simulation set is used
%to estimate both $\bbh{C},\bbh{\Psi}$, these errors tend to decrease
%with $N_b$ (case 2), or at best remain constant (case 3), while the
%distribution of $\bbh{p}$ has still a variance that increases with
%$N_b$. This typically leads to underestimates in parameter errors. 
%AP: Not exactly: my point was that the distribution of \bbh{p} has a true variance that increases with Nb, but the estimate of this variance (which we quote as the errorbar) does not increase with Nb. Hence we get the wrong parameter fit (i.e. which excludes the true value at high significance level)
%ZH2: OK.  I think by `` the parameter estimate $\bbh{p}$ has a variance that grows linearly with $N_b$,'' you mean equation 10
%   (i.e.  technically it is [variance-1] grows linearly with N_b.   I rephrased below to say ``whose noise'' grows linearly and
% cite eq.10.    OK?
Note that in the last case, which is most relevant when fitting actual
data, the estimated degradation turns out to be too optimistic: the
parameter estimate $\bbh{p}$ has a variance whose noise grows linearly
with $N_b$ (eq.~\ref{quarticdegradation}), whereas the degradation
estimated via eq. (\ref{mockscalingcorrected}) is constant with
$N_b$. This can lead to underestimation of error bars, which can be
mistakenly interpreted as a parameter bias.  We derived the scaling
relations of the form
%
\begin{equation}
\label{ourscaling}
\langle\h{\sigma}_p^2\rangle = \sigma^2_{p,\infty}(N_s)\left(1+\frac{D}{N_r}\right)
\end{equation}
%
above by assuming that the noise in $\bbh{d}$ is Gaussian. We then
directly test these scaling relations using our simulations, in the
limits of both high and low $N_r$.
%ZH: It is still a little unclear here what is being tested.  Is it the Gaussianity assumption? I added that.
%    But perhaps you had some other issue in mind.
%AP: The noise in $\bbh{C}$ and $\bbh{\Psi}$ is not Gaussian: if the data vector from which $\bbh{C}$ and $\bbh{\Psi}$ are estimated in Gaussian, then these matrices are distibuted according to, respectively, the Wishart and inverse Wishart distributions. We are testing that the degradation effectively decreases as 1/Nr at leading order.  
%ZH2: I am still confused.  What is it that could go wrong?   I.e. do you have something in mind that could cause a departure from this 1/N_r
%     scaling?    That is what we are testing, then, but I am not sure what it is.   Are we testing whether the simulations could have a bug?  
%     Or maybe you simply are testing the validity of truncating the expansion at second order in DeltaPsi ?   
%     Or maybe what you have in mond is the possible importance of high-order terms in the expansion (beyond the quartic terms, 
%     and beyond 1/N_r^2) could cause a deviation from 1/N_r that is different from the 1/N_r^2 term in eq.10 ?  In other words,
%     then we're testing for the importance of the 1/N_r^3 and higher terms numerically...  is that your point?
%
We indicate the diagonal elements of $\h{\Sigma}_{\bb{p}}$ as
$\h{\sigma}^2_p=\mathrm{diag}(\h{\Sigma}_{\bb{p}})$ and we indicate by
$\sigma^2_{p,\infty}$ the expectation value of the variance of each
parameter in the limit of an infinite number of realizations
$N_r\rightarrow\infty$.  We call $D$ the \textit{effective
  dimensionality} of the feature space (which, as seen before, can be
negative in some pathological cases).  We compute the expectation
values of $\h{\sigma}^2_p$ (eqs.~\ref{estimatorcovariance} and
\ref{ourscaling}) by averaging over 100 random resamplings of our
shear ensembles. For the true feature covariance matrix
$\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use
the estimated covariance from a grand ensemble built with the union of
all the ensembles with different $N_s$.

@@

In this section we discuss our main findings and their
implications. Figure \ref{ps_pdf} shows that, although different
choices of $N_s$ do not affect the power spectrum PDF on large scales
(top two panels), there are some qualitative differences on smaller
scales (bottom two panels). On these smaller scales, shear ensembles
built from $N_s=1$ do not produce the same statistical behavior as
ensembles built with larger $N_s$. In particular, looking at the black
curves, we see that the $N_s=1$ ensembles exibit large shifts with
respect to the other PDFs to lower power, including the locations of
the peaks of the PDFs.  We attribute these offsets to large (random)
statistical errors.
